\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-05-31 paper/paper.tex
Morning changes

\begin{figure}[H]
\includegraphics[width=\textwidth]{fig/data_sum.pdf}
\caption{Left: Total number of failures (log scale) for drive-models with at least 3 observed failures in the Backblaze data. Right: Total time in operation (log scale) for each of the drive-models in the Backblaze data.  Both plots are sorted based on the total number of failures.}
\label{fig1}
\end{figure}

@@

Applying this method to the hard drive data, we first must estimate the empirical cdf for each model using the Kaplan-Meier estimator \cite{kaplan}.  With left truncation, however, the standard Kaplan-Meier estimator for drive-model $d$, denoted by $\widehat{F_d(t)}_{KM}$, is conditional on survival up to $t_{d,\text{min}}^L$, the shortest reported running time of all units of drive-model $d$ for which records are available. To produce unconditional estimates, we adapt the adjustment method outlined by Turnbull, and given in more detail by Meeker and Escobar \cite{turnbull,meeker}.  For each hard drive model we select $t_{d,\text{min}}^L$, the smallest left truncated time in the sample.  By sampling from the full posterior distribution, since $Pr(T>t_{d,\text{min}}^L|\theta_d)$ (the probability a hard drive has survived up to $t_{d,\text{min}}^L$) is a function of the model parameters, we can easily compute its posterior median, $\widehat{A}_{\text{med}} = \widehat{Pr}_(T>t_{d,\text{min}}^L|\theta_d)$. We compute the adjusted estimate by

@@

%\begin{figure}
%\includegraphics[width=.8\textwidth]{fig/data_overview}
%\caption{Left: Kaplan-Meier plots showing nonparametric estimates of fraction failing for individual drive-models with truncation adjustments based on fitted model, Right: Total observed failures (top) and the sum of lengths of all observational intervals by drive-model.}
%\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=.5\textwidth]{fig/mod14_KM_adj}
\caption{Truncated Adjusted Kaplan-Meier plot showing nonparametric estimate of fraction failing for drive model 14.  Dashed lines are Greenwood standard errors.  Plotted on Weibull paper.}
\end{figure}

@@

To borrow strength across models, we can either share parameters across drive-models, or model the drive-model specific parameters hierarchically, allowing the data to inform the hyperparameters. For the second option, we model the scales, $\sigma_j$, quantiles, $t_{p_j,d,j} = \Phi^{-1}(\mu_j)$, and proportions, $\pi_d$, of the component distributions as follows:

$$\sigma_{d,1} \ind \op{Lognormal} \left( \eta_{\sigma,1}, \tau^2_{\sigma,1} \right) \mbox{ for } d=1,\ldots,D$$
$$\sigma_{d,2} \ind \op{Truncated-Lognormal} \left( \eta_{\sigma,2}, \tau^2_{\sigma,2} , 0, 1, \right) \mbox{ for } d=1,\ldots,D$$
$$t_{p_j,d,j} \equiv \mu_{d,j} + \sigma_{d,j}\,\Phi^{-1}(p_j)  \ind \op{Normal} \left(\eta_{t_{p_j},j}, \tau^2_{t_{p_j},j}\right) \mbox{ for } j=1,2\; d=1,\ldots,D$$

$$\op{logit} \pi_d \ind \op{N}(\eta_pi, \tau_pi) \mbox{ for } d=1,\ldots,D.$$

@@

\subsection{Model Comparisons}
\begin{figure}
\includegraphics[width=\textwidth]{fig/heterogeneity_compare_preliminary.pdf}
\caption{Left: Kaplan-Meier estimates of the time to failure for each of the drive-models in the Backblaze data. Right: Pointwise posterior median time to failure curves for Models 1-4, orderered left to right, top to bottom.}
\label{fig2}
\end{figure}

@@

\begin{figure}[H]
    \centering
   \includegraphics[width=5.0in]{fig/brand_compare_nobands.pdf}
		\caption{Estimated GFLP for all 4 Model Specifications.  Truncated Adjusted Kaplan Meier points are also presented.    \label{fig:first}} 
\end{figure}

@@

\subsection{Brand Comparisons}

\begin{figure}[H]
\centering
 \includegraphics[width=4.0in]{fig/b10andpi.pdf}
\caption{Left: 50\% credible intervals for B10 (time in years till 10\% of the drives fail). Right: 50\% credible intervals for $\pi$ plotted on the logit scale.  Both plots are sorted based on the median value of B10.}
\label{fig4}
\end{figure}

>>>>

\begin{figure}[H]
\includegraphics[width=\textwidth]{fig/data-sum.pdf}
\caption{Left: Total number of failures (log scale) for drive-models with at least 3 observed failures in the Backblaze data. Right: Total time in operation (log scale) for each of the drive-models in the Backblaze data.  Both plots are sorted based on the total number of failures.}
\label{fig1}
\end{figure}

@@

Applying this method to the hard drive data, we first must estimate
the empirical cdf for each model using the Kaplan-Meier estimator
\cite{kaplan}.  With left truncation, however, the standard
Kaplan-Meier estimator for drive-model $d$, denoted by
$\widehat{F_d(t)}_{KM}$, is conditional on survival up to
$t_{d,\text{min}}^L$, the shortest reported running time of all units
of drive-model $d$ for which records are available. To produce
unconditional estimates, we adapt the adjustment method outlined by
Turnbull, and given in more detail by Meeker and Escobar
\cite{turnbull,meeker}.  For each hard drive model we select
$t_{d,\text{min}}^L$, the smallest left truncated time in the sample.
By sampling from the full posterior distribution, since
$Pr(T>t_{d,\text{min}}^L|\theta_d)$ (the probability a hard drive has
survived up to $t_{d,\text{min}}^L$) is a function of the model
parameters, we can easily compute its posterior median,
$\widehat{A}_{\text{med}} = \widehat{Pr}(T>t_{d,\text{min}}^L|\theta_d)$. We compute the adjusted estimate by

@@

%\begin{figure}
%\includegraphics[width=.8\textwidth]{fig/data-overview}
%\caption{Left: Kaplan-Meier plots showing nonparametric estimates of fraction failing for individual drive-models with truncation adjustments based on fitted model, Right: Total observed failures (top) and the sum of lengths of all observational intervals by drive-model.}
%\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=.5\textwidth]{fig/mod14-KM-adj}
\caption{Truncated Adjusted Kaplan-Meier plot showing nonparametric estimate of fraction failing for drive model 14.  Dashed lines are Greenwood standard errors.  Plotted on Weibull paper.}
\end{figure}

@@

To borrow strength across models, we can either share parameters across drive-models, or model the drive-model specific parameters hierarchically, allowing the data to inform the hyperparameters. For the second option, we model the scales, $\sigma_j$, quantiles, $t_{p_j,d,j}$, and proportions, $\pi_d$, of the component distributions as follows:

$$\sigma_{d,1} \ind \op{Lognormal} \left( \eta_{\sigma,1}, \tau^2_{\sigma,1} \right) \mbox{ for } d=1,\ldots,D$$
$$\sigma_{d,2} \ind \op{Truncated-Lognormal} \left( \eta_{\sigma,2}, \tau^2_{\sigma,2} , 0, 1 \right) \mbox{ for } d=1,\ldots,D$$
$$t_{p_j,d,j} \equiv \mu_{d,j} + \sigma_{d,j}\,\Phi^{-1}(p_j)  \ind \op{Normal} \left(\eta_{t_{p_j},j}, \tau^2_{t_{p_j},j}\right) \mbox{ for } j=1,2\; d=1,\ldots,D$$

$$\op{logit} \pi_d \ind \op{N}(\eta_\pi, \tau_\pi) \mbox{ for } d=1,\ldots,D.$$

@@

\subsection{Model Comparisons}
\begin{figure}
\includegraphics[width=\textwidth]{fig/heterogeneity-compare-preliminary}
\caption{Left: Kaplan-Meier estimates of the time to failure for each of the drive-models in the Backblaze data. Right: Pointwise posterior median time to failure curves for Models 1-4, orderered left to right, top to bottom.}
\label{fig2}
\end{figure}

@@

\begin{figure}[H]
    \centering
   \includegraphics[width=5.0in]{fig/brand-compare-nobands}
		\caption{Estimated GFLP for all 4 Model Specifications.  Truncated Adjusted Kaplan Meier points are also presented.    \label{fig:first}} 
\end{figure}

@@

\subsection{Drive-model Comparisons}
We consider the problem of selecting between drive-models. From the
perspective of return on investment, is clear
that we should prefer the drive-models which will provide more years
of service. There are two sources of variation at play; the
posterior uncertainty in the parameters, which largely depends on the
sample size, and the uncertainty in future
observations conditional on the parameters. The {\em posterior
  predictive} distribution incorporates both sources.
\begin{equation}

\end{equation}

Figure \ref{fig5} shows the predi

\begin{figure}[H]
  \centering
  \includegraphics[width=.8\textwidth]{fig/b10andpi}
  \caption{Left: 50\% credible intervals for B10 (time in years till 10\% of the drives fail). Right: 50\% credible intervals for $\pi$ plotted on the logit scale.  Both plots are sorted based on the median value of B10.}
  \label{fig4}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=.8\textwidth]{fig/dm-eval}
  \caption{Left: Posterior predictive TTF (years) for new
    unit, by drive-model. Right: TTF (top) and loss based on exponential
    devaluation, $\lambda=5$ (bottom), for best 11 drive-models.}
  \label{fig5}
\end{figure}
